---
title: "Competition dashboard"
output: html_document
params:
  n: NA
  p1_name : NA
  p1_conc : NA
  p1_mol_weight : NA
  p2_name : NA
  p2_conc : NA
  p2_mol_weight : NA
  p1unit: NA
  p2unit: NA
  comp_name : NA
  comp_conc : NA
  comp_unit : NA,
  comp_mol_weight : NA
  kd : NA
  ki : NA
  plot1 : NA
  plot2 : NA
  plot3 : NA
  plot4 : NA
  table1 : NA
  table2 : NA
  table3 : NA
  table4 : NA
  namep1 : NA
  namep2 : NA
  namep12 : NA
  namep22 : NA
  container : NA
 
---


\
\
`r toString(params$p1_name)`: `r toString(params$p1_conc)` (`r toString(params$p1unit)`)\
Molecular weight of partner 1 : `r toString(params$p1_mol_weight)` (dalton)\
`r toString(params$p2_name)` : `r toString(params$p2_conc)` (`r toString(params$p2unit)`)\ 
Molecular weight of partner 2 : `r toString(params$p2_mol_weight)` (dalton)\
`r toString(params$comp_name)` : `r toString(params$comp_conc)` (`r toString(params$comp_unit)`)\ 
Molecular weight of the competing partner : `r toString(params$p2_mol_weight)` (dalton)\
Kd : `r toString(params$kd)`\
Ki : `r toString(params$ki)`\
\
\
\
\


  
```{r echo=FALSE, cache=FALSE, warning = FALSE, message = FALSE, tidy=TRUE, fig.width=12,fig.height=7} 

if(is.null(webshot:::find_phantom())){
webshot::install_phantomjs()
} 

#PLOT 1  
ggplotly(params$plot1)
```
\

```{r echo=FALSE, cache=FALSE, warning = FALSE, message = FALSE, tidy=TRUE, fig.width=12,fig.height=7} 

sketch <- params$container(params$namep1, params$namep2, params$table1)

#TABLE 1
datatable(
  params$table1,
  container = sketch,
  rownames = FALSE, 
  options = list(dom = 't')
 )%>%
  formatStyle(params$table1 [ ,1], fontWeight = "bold")
```
\
\
\
\

```{r echo=FALSE, cache=FALSE, warning = FALSE, message = FALSE, tidy=TRUE, fig.width=12,fig.height=7} 
#PLOT 2  
ggplotly(params$plot2)
```

\


```{r echo=FALSE, cache=FALSE, warning = FALSE, message = FALSE, tidy=TRUE, fig.width=12,fig.height=7}   
sketch <- params$container(params$namep1, params$namep2, params$table2)

#TABLE 2
datatable(
  params$table2,
  container = sketch,
  rownames = FALSE, 
  options = list(dom = 't')
 )%>%
  formatStyle(params$table2 [ ,1], fontWeight = "bold")

```
\
\
\
\



```{r echo=FALSE, cache=FALSE, warning = FALSE, message = FALSE, tidy=TRUE, fig.width=12,fig.height=7} 
#PLOT 3  
ggplotly(params$plot3)
```
\

```{r echo=FALSE, cache=FALSE, warning = FALSE, message = FALSE, tidy=TRUE, fig.width=12,fig.height=7} 
sketch <- params$container(params$namep12, params$namep22, params$table3)
#TABLE 3
datatable(
  params$table3,
  container = sketch,
  rownames = FALSE, 
  options = list(dom = 't')
 )%>%
  formatStyle(params$table3 [ ,1], fontWeight = "bold")
```
\
\
\
\


```{r echo=FALSE, cache=FALSE, warning = FALSE, message = FALSE, tidy=TRUE, fig.width=12,fig.height=7} 

#PLOT 4  
ggplotly(params$plot4)
```
\


```{r echo=FALSE, cache=FALSE, warning = FALSE, message = FALSE, tidy=TRUE, fig.width=12,fig.height=7} 

ketch <- params$container(params$namep12, params$namep22, params$table4)

#TABLE 4
datatable(
  params$table4,
  container = sketch,
  rownames = FALSE, 
  options = list(dom = 't')
 )%>%
  formatStyle(params$table4 [ ,1], fontWeight = "bold")
```



```


